\documentclass[11pt,a4paper,sans]{moderncv}        
\moderncvstyle{classic}
\moderncvcolor{green}                              
\usepackage[utf8]{inputenc}
\usepackage[scale=0.90]{geometry}
\name{Dominik}{Moštěk}
\title{Curriculum Vitae}
\phone[mobile]{+420 728962386}
\email{mostekdominik@gmail.com}
\linkedin{http://cz.linkedin.com/in/dominikmostek}
\github{https://github.com/DominikMostek}
\begin{document}
\makecvtitle

\section{Experience}
\cventry{2015--now}{Senior software engineer}{DHL Information Services Europe s.r.o.}{Prague}{}{I have worked on Test automation project and several other small projcts which included changes to older systems.}
\cventry{2014--2015}{Senior Java Developer and Analyst}{Home Credit International a.s.}{Prague}{}{I have worked on project MUCH and became leader of the team of several developers for this project. I also developed mobile application store, alternative to google play.}
\cventry{2012--2014}{Java developer}{AspectWorks s.r.o}{Prague}{I enterd as an java developer trainee then i became full time enterprise java developer.
\newline
I was also maintaining company blog, twitter and facebook accounts}{}
\cventry{2012}{Linux server administrator}{SuperHosting s.r.o}{Prague}{}{I was responsible for installing new servers and resolving issues that occured on the running ones}
\cventry{Before 2012}{PHP Programmer}{4Stones s.r.o, Firis s.r.o, Inventive Designs, ePortaly.cz}{Prague}{}{I was programming various websites, including eshop and reservation systems.}

\section{Education}
\cventry{2009--2013}{Czech Technical University}{Not finished}{Prague}{\textit{}}{My field of study was Software engineering and management. I finished almost all classes but left because of work.}
\cventry{2005--2009}{High School of Electrical Engineering}{Secondary school}{Praha}{\textit{Graduated}}{My field of study was Information technology, specialization in programming.}

\section{Languages}
\cvitemwithcomment{Czech}{Native speaker}{}
\cvitemwithcomment{English}{Upper Intermediate}{I use english everyday in personal life and in work.}
\cvitemwithcomment{German}{Beginer}{I started to learn german in 2015.}

\section{Programming skills}
\subsection{Languages}
\cvitem{Java}{Oracle Certified Professional and Java is my main language currently.}
\cvitem{Groovy}{Groovy is my first choice when it comes to unit tests.}
\cvitem{SQL}{I Like to use plain SQL in my applications and i have good experience with difficult queries.}
\cvitem{PHP, Ruby, Python}{I have written websites, tools and various programs using theese languages. Python is my \#1 for scripts and solving mathemtical problems.}
\cvitem{\texttt{C++}}{Only occasional usage}
\cvitem{\texttt{Clojure}}{I have just started to learn functional programming and Clojure}
\subsection{Approach}
\cvitem{\texttt{TDD}}{I am big envangelist of test driven development.}
\cvitem{\texttt{OOP}}{In J2EE applications its rare to see real OOP and i tend to change this trend. I love to use DDD and CQRS approach to design applications.}
\cvitem{\texttt{CleanCode}}{Readable and maintainable code is my main target.}
\cvitem{Agile}{Agile approach has a great benefit for most projects I have worked on and i try to introduce this mindset in other projects.}
\subsection{Tools, Frameworks}
\cvitem{Spring}{I am building most of the java project using spring, spring mvc/security/integration and other parts of spring frmaework.}
\cvitem{Android}{I have developed two Android applications and contibuted to two others.}
\cvitem{Hibernate, JPA}{I am using JPA as an interface and hibernate as an orm engine on almost all projects.}
\cvitem{JSF, Primefaces}{I am not a big fan of this projects but i used it on two projects and gained a lot of experience with them.}
\cvdoubleitem{Build tools}{Maven, Gradle}{Testing frameworks}{Junit, EasyMock, Spock}
\subsection{Metodologies}
\cvitem{Scrum}{My favorite metodology. Most of project i did was developed using this metodology.}
\cvitem{Kanban}{Used on two projects so far.}
\cvitem{eXtreme programming}{I do not stick to all of XP points but to most of them. For example Continuos integration, Test driven development, agility and customer interaction.}
\subsection{Others}
\cvitem{Linux}{I am user and big fan of gnu/linux systems.}
\cvitem{Servers}{Installation/Administration of Tomcat, Apache, MySQL, Postgres}

\section{Project references}
\cvitem{Test automation}{Solution for automatization of testing several projects in DHL. It consisted of Cucumber scenarios, Jenkins servers with custom plugins.}
\cvitem{MUCH}{System which controlled the employees in field and drived where they should go and what to do there. Part of this project was android tablet application which was used to record data from the visit.}
\cvitem{MLP Android app}{This is my open-source project. It is mobile application for municipal library of Prague.}
\cvitem{HitHit}{www.hihit.com - crowd-funding server. I was responsible for development of payment system.}
\cvitem{Orinoco}{Internal software of AspectWorks. It is software for managing company processes (BPM).}
\cvitem{Jablotron Kruh}{Software for security cars management for company Jablotron.}
\cvitem{DHL Configuration center}{Configuration center of the DHL integration framework.}
\cvitem{DHL eBilling}{Software for invoicing and integration with customers.}

\section{Interests}
\cvitem{}{I love programming and software development, i like to talk about it, learn new technologies and also spread my knowledge. I attend IT meetups, talks, conferences and other social events. I also love sports, mainly cycling, fitness and snowboarding. My big passion is traveling.}

\nocite{*}
\bibliographystyle{plain}
\clearpage
\end{document}